NTIRE 2023 Real-Time Super-Resolution

### 2023-03-18 NTIRE 2023 Efficient SR Challenge Factsheet/EfficientSR_factsheet.tex
基本信息

%%%%%%%%% TITLE - PLEASE UPDATE
\title{NTIRE 2023 Efficient SR Challenge Factsheet\\-title of the contribution-}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}
\maketitle

@@

\begin{itemize}
\item Team name                                  
\item Team leader name                           
\item Team leader address, phone number, and email 
\item Rest of the team members        
\item Team website URL (if any)                   
\item Affiliation
\item Affiliation of the team and/or team members with NTIRE 2023 sponsors (check the workshop website)
\item User names and entries on the NTIRE 2023 Codalab competitions (development/validation and testing phases)
\item Best scoring entries of the team during development/validation phase
\item Link to the codes/executables of the solution(s)
\end{itemize}

>>>>

%%%%%%%%% TITLE - PLEASE UPDATE
\title{NTIRE 2023 Efficient SR Challenge Factsheet\\PRFDN: High Parallelism Distillation Network For Image Super-resolution}

\author{Daheng Yin, Baijun Chen, Mengyang Liu\\
School of Computer Science and Engineering, Southeast University\\
Nanjing, Jiangsu\\
{\tt\small {yindaheng98, bjchen, myliu}@seu.edu.cn}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

@@

\begin{itemize}
\item Team name: SEU\_CNII
\item Team leader name: Daheng Yin
\item Team leader address, phone number, and email: \\School of Computer Science and Engineering, Southeast University; \\+86 188 5189 9135; yindaheng98@seu.edu.cn
\item Rest of the team members: Baijun Chen, Mengyang Liu
\item Team website URL (if any): N/A
\item Affiliation: School of Computer Science and Engineering, Southeast University
\item User names and entries on the NTIRE 2023 Codalab competitions (development/validation and testing phases): yindaheng98
\item Best scoring entries of the team during development/validation phase:\\PSNR 28.993
\item Link to the codes/executables of the solution(s): \url{https://github.com/yindaheng98/NTIRE23-RTSR}
\end{itemize}

### 2023-03-18 NTIRE 2023 RTSR Factsheet/main.tex
基本信息

%%% Add Your names and affiliations.
\author{\textcolor{red}{Your Teamname Here}\\
\textcolor{red}{Your names}\thanks{\textcolor{blue}{Affiliations}}\\
}

@@

\begin{itemize}
\item Team name                                  
\item Team leader name                           
\item Team leader institution and email (Please make sure is an active email)
\item Rest of the team members        
\item Team website URL (if any)                   
\item Affiliations
\item Usernames on the NTIRE 2023 Real-Time Super-Resolution Codalab leaderboard (development/validation and testing phases)
\item Link to the codes/executables of the solution(s) following \url{https://github.com/eduardzamfir/NTIRE23-RTSR}
\end{itemize}

@@

\begin{itemize}
\item Title of the contribution
\item General method description (Summary)
\item References                                               
\item have you tested previously published methods? (yes/no) If yes, please specify which methods and the results/problems you found.
\item Other methods and baselines tested (even if results were not top competitive).
\end{itemize}

>>>>

%%% Add Your names and affiliations.
\author{\textcolor{red}{SEU\_CNII}\\
\textcolor{red}{Daheng Yin, Baijun Chen, Mengyang Liu}\thanks{\textcolor{blue}{School of Computer Science and Engineering, Southeast University}}\\
}

@@

\begin{itemize}
\item Team name: SEU\_CNII
\item Team leader name: Daheng Yin
\item Team leader institution and email: School of Computer Science and Engineering, Southeast University; yindaheng98@seu.edu.cn
\item Rest of the team members: Baijun Chen, Mengyang Liu
\item Team website URL (if any): N/A
\item Affiliations: School of Computer Science and Engineering, Southeast University
\item Usernames on the NTIRE 2023 Real-Time Super-Resolution Codalab leaderboard (development/validation and testing phases): yindaheng98
\item Link to the codes/executables of the solution(s) following \url{https://github.com/yindaheng98/NTIRE23-RTSR}
\end{itemize}

@@

\begin{itemize}
\item Title of the contribution\\PRFDN: High Parallelism Distillation Network For Image Super-resolution
\item General method description (Summary)
\item References                                               
\item have you tested previously published methods? (yes/no) If yes, please specify which methods and the results/problems you found.
\item Other methods and baselines tested (even if results were not top competitive).
\end{itemize}
